What is the Effect of X on Y?

### 2022-04-05 latex-slides/slides.tex
Add \begin{transitionframe}
Update article and slides
Fixes
- Fix subtitle requirement
- Add color commands
- Add bgColor boxes

% Title --------------------------------------------
\title{What is the Effect of X on Y?}
\subtitle{Evidence from a Personal Anecdote}
\date{\today}
\author{Kyle Butts}

@@

@@

@@

\begin{frame}{Components}{Colors}
    {\color{navy} Test sentence with \textbackslash color\{navy\}}\newline
    {\color{purple} Test sentence with \textbackslash color\{purple\}}\newline
    {\color{kelly} Test sentence with \textbackslash color\{kelly\}}\newline
    {\color{ruby} Test sentence with \textbackslash color\{ruby\}}\newline
    {\color{alice} Test sentence with \textbackslash color\{alice\}}\newline
    {\color{daisy} Test sentence with \textbackslash color\{daisy\}}\newline
    {\color{coral} Test sentence with \textbackslash color\{coral\}}\newline
    {\color{cranberry} Test sentence with \textbackslash color\{cranbery\}}\newline
    {\color{slate} Test sentence with \textbackslash color\{slate\}}\newline
    {\color{jet} Test sentence with \textbackslash color\{jet\}}\newline
    {\color{asher} Test sentence with \textbackslash color\{asher\}}\newline
\end{frame}

>>>>

% Title --------------------------------------------
\title{What is the Effect of X on Y?}
\date{\today}
\author{Kyle Butts}

@@

\begin{transitionframe}
Transitioning Sentence
\end{transitionframe}

@@

        \begin{itemize}
            \item This allows you to draw attention to specific words/phrases
        \end{itemize}

@@

\begin{frame}{Components}{Colors}
  \navy{Test sentence with \textbackslash navy\{...\}}

  \purple{Test sentence with \textbackslash purple\{...\}}

  \kelly{Test sentence with \textbackslash kelly\{...\}}

  \ruby{Test sentence with \textbackslash ruby\{...\}}

  \alice{Test sentence with \textbackslash alice\{...\}}

  \daisy{Test sentence with \textbackslash daisy\{...\}}

  \coral{Test sentence with \textbackslash coral\{...\}}

  \cranberry{Test sentence with \textbackslash color\{cranbery\}}

  \slate{Test sentence with \textbackslash color\{slate\}}

  \jet{Test sentence with \textbackslash color\{jet\}}

  \asher{Test sentence with \textbackslash color\{asher\}}
\end{frame}

\begin{frame}{Components}{Colored Boxes}
  \bgNavy{Test word} with \textbackslash bgNavy\{...\}

  \vspace{2.5mm}
  \bgPurple{Test word} with \textbackslash bgPurple\{...\}

  \vspace{2.5mm}
  \bgKelly{Test word} with \textbackslash bgKelly\{...\}

  \vspace{2.5mm}
  \bgRuby{Test word} with \textbackslash bgRuby\{...\}

  \vspace{2.5mm}
  \bgAlice{Test word} with \textbackslash bgAlice\{...\}

  \vspace{2.5mm}
  \bgDaisy{Test word} with \textbackslash bgDaisy\{...\}

  \vspace{2.5mm}
  \bgCoral{Test word} with \textbackslash bgCoral\{...\}

  \vspace{2.5mm}
  \bgCranberry{Test word} with \textbackslash bgCranberry\{...\}
\end{frame}
